Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-07-28 manuscript_results.Rmd
update

  # Sum values by Julian date across all states
  mean_improvement_ <- combined_dataframes_ %>%
    group_by(Julian_date) %>%
    summarize(
      AUTO_AR = mean(AUTO_AR, na.rm = TRUE),  # Sum across all states
      AUTO_AVG_LB = mean(AUTO_AVG_LB, na.rm = TRUE)           # Sum across all states
    ) %>%
    # Calculate the difference ratio in percentage
    mutate(Difference =  ((AUTO_AVG_LB / AUTO_AR)-1)*100,
           Week = paste0("Week ", week))

>>>>

  # Sum values by Julian date across all states
  mean_improvement_ <- combined_dataframes_ %>%
    group_by(Julian_date) %>%
    summarize(
      AUTO_AR = mean(AUTO_AR, na.rm = TRUE),  # Mean across all states
      AUTO_AVG_LB = mean(AUTO_AVG_LB, na.rm = TRUE) # Mean across all states
    ) %>%
    # Calculate the difference ratio in percentage
    mutate(Difference =  ((AUTO_AVG_LB / AUTO_AR)-1)*100,
           Week = paste0("Week ", week))
